### 2023-02-22 paper.tex
added VR

    \subsection{VR}

        (p2)

>>>>

    \subsection{VR}
        A new method of robot programming attempts to combine the advantages of online and offline concepts. The idea is to use Virtual Reality to define needed motion sequences offline via simulation without any effort for the programmer. Therefore "the desired waypoints can be intuitively defined and checked in the virtual environment and stored through buttons and menus."  \cite[625]{p2} The simulation is not suitable for small changes in the motion path, which is why Online-Programming might still be needed because it allows a fine-tuning directly in the targeted manufacturing process.  However, if further changes or updates are required, the programme can be transferred back to offline simulation, which is a key advantage over traditional online programming as the robot does not need to be stopped within the process. \cite[625]{p2}
